How do changes in ex vary between countries?

### 2022-03-01 draft_paper.Rmd
added line to analysis
Additional_text
Added some additional text on data, methods and analyses inc. time-trend

For each of these countries, and for males and females separately, we are interested in the annual changes in life expectancy at birth ($e_0$) and life expectancy at age 65 ($e_{65}$), from 1980 to the last available year for each country.

@@

The following shows life expectancy at birth and at age 65 for selected nations:

@@

## Change in life expectancy in these nations

@@

# Time trends

@@

>>>>

For each of these countries, and for males and females separately, we are interested in the annual changes in life expectancy at birth ($e_0$) and life expectancy at age 65 ($e_{65}$), from 1980 to the last available year for each country. In addition, we compare average life expectancy improvements over the 4 decades: 1980, 1990, 2000, and 2010.

@@

The following figures show life expectancy at birth and at age 65 for selected nations from 1980 to the latest available year.

@@

## Change in life expectancy in these nations 
Next, we compare the annual change in life expectancy at birth and at aged 65 years for the 6 nations from 1980 to the latest available year, by sex.

@@

# Time trends 
Finally, we used time-trend analysis to explore the changes in life expectancy over the 4 decades: 1980s, 1990s, 2000s, and 2010s. This produces the average change for the decade, whether negative or positive, the standard error and its statistical significance for each country by sex.

@@

# Discussion
Limitations: fewer years for comparison in 2010s; comparing different time periods will provide different results.
